---
title       : Developing Data Products Project
subtitle    : Pitching my Simple Stock App
author      : ichew
job         : R Beginner
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Project Pitch

You may have read that the movie Avengers: Age of Ultron have crossed the $1 billion mark in box-office worldwide after 15-May-2015.

As this movie is owned by Disney, wouldn't you like to know how Disney stock prices react to this news? Has Disney stock price been trending up even before this movie's release?

You can answer these questions and more using my Simple Stock App.

I have embedded the app in the next slide.

Have fun and May The Force Be with You! 
(Will Disney's next blockbuster Star Wars boost its price?)

--- .class #id 

## Simple Stock App linked from shinyapps.io

<iframe src="https://ichew.shinyapps.io/_dataproducts/">
</iframe>

--- .class #id 

## Running embedded R Code (1/2)

Below is an R expression that will be run in the next slide.

It extracts 5 days Disney stock prices from yahoo and plot a simple candlestick chart.

This is to fulfil the requirements "Did it contain an R expression that got evaluated and displayed?".

```{r eval=FALSE}
options(warn=-1)
library(quantmod)
dis_env <- new.env()
getSymbols("DIS", env = dis_env, src = "yahoo", 
           from = as.Date("2015-05-04"), to = as.Date("2015-05-08"))
vDIS <- dis_env$DIS
chartSeries(vDIS, name = "Disney", type = "candlesticks", 
            theme = chartTheme("black"), up.col = "lightblue", dn.col = "red",TA=NULL                  
            )
```

--- .class #id 

## Running embedded R Code (2/2)

```{r echo=FALSE, results = 'asis', fig.height=5}
options(warn=-1)
library(quantmod)
dis_env <- new.env()
getSymbols("DIS", env = dis_env, src = "yahoo", from = as.Date("2015-05-04"), to = as.Date("2015-05-08"))
vDIS <- dis_env$DIS
names(vDIS)[names(vDIS)==""] <- "date"

chartSeries(vDIS,
            name = "Disney",                                     
            type = "candlesticks", 
            theme = chartTheme("black"),
            up.col = "lightblue",
            dn.col = "red",
            TA=NULL                  
            )
```
